\textbf{SYNOPSIS}

### 2017-04-27 intro.tex
final changes
review corrections

\section{Optimization methods via simulation }\label{sc:dis}
Optimization via simulation is a fast developing area for both researchers and practioners. As mentioned before, for stochastic optimization problems, simulation is a viable approach compared. Multiple simulation replications must be performed in order to get a good estimate of $E_{\xi}[h(\theta_i,\xi)]$, which is the function value at parameter $\theta_i$. The standard approach to estimate this is via the sample mean
\begin{align}\label{eq:sm}
\overline {f_n} (\theta_i) = \frac{1}{n} ~  \sum_{j=1}^{n} h(\theta,\xi_j),
\end{align}
where $n$ is the number of simulation replications and $\xi_j$ is the $j$th sample of randomness. As $n \to \infty$, $\overline{ f_n} (\theta_i) \to E_{\xi}[h(\theta_i,\xi)]$. The primary concerns in stochastic optimization via simulation are 
\begin{inparaenum}[\bfseries (i)]
	\item $n$ must be large enough to get a good estimate of  $E_{\xi}[h(\theta_i,\xi)]$, which has an impact on the final solution that the optimization procedure needs to find; and
	\item The above procedure must be applied for many different parameters, i.e., $\theta$'s in order to find the best $\theta$.
\end{inparaenum}
Hence one of the key criteria for comparing different simulation-based optimization approaches is through the total number of simulations performed by them to attain a specific function value. Note that different approaches may require different number of simulations per  iteration. In this section we present methods only for Continuous and Discrete optimization via simulation problems which often occur in practise. However, hybrid optimization problems are not frequently encountered. From  now on, we consider the setting of optimization problems mentioned in this section as the stochastic optimization setting presented in section \ref{sc:objclass}, i.e., when objective function is an expected value over certain noisy cost measurements. 
\subsection{Discrete optimization via simulation}
Optimization problems for which $\Theta$ is a discrete set are known as discrete optimization via simulation problems. In the discrete case $\theta$, can take only countable (finite or infinite) number of values. Discrete optimization problems are some times take the form of \emph{combinatorial optimization} problems and they have applications in resource allocation, network routing, policy planning etc.
In this section we consider the case of $\Theta$ being finite i.e., $\Theta = \{\theta_{1},\theta_{2},\ldots,\theta_{k}\}$ where $k \in \mathbb{N}$. Discrete optimization problems are divided into two sub-classes when the feasible region is  either small (often less than 100) or is large. We present optimization methods in the literature separately for each class.\\
%\begin{enumerate}
\subsubsection{$\Theta$ is small}
In this case we can simulate all possible solutions and select the best among them. However, unlike in deterministic optimization, simulating the system only once for each parameter is not enough since the objective function is noisy in the stochastic optimization setting. Hence the main question is how to conduct multiple simulations effectively for each parameter in order to determine the  best parameter $\theta$.  Two popular methods in literature for this case are Ranking and Selection (R\&S)\cite{bech} and Multiple comparison procedures (MCP) \cite{mcp}. These methods are well suited for simulation since  the underlying assumptions such as normality and independence of observations can be met through careful selection procedures.
Traditional methods in this setting are applicable for a maximum set size of 20 while some recent techniques allow more. 
\begin{enumerate}

@@

where $a_n$ is the step-size that satisfies standard stochastic approximation conditions (see (A12) in Section \ref{sec:2rdsa-results}), and $\widehat\nabla f(\theta_n)$ and $\overline H_n$ are estimates of the gradient and Hessian, respectively. Thus, \eqref{eq:newton} can be considered as  the stochastic version of the well-known Newton method for optimization. Stochastic Newton methods are often more accurate than simple gradient search schemes.

>>>>

\section{Optimization methods via simulation }\label{sc:dis}
Optimization via simulation is a fast developing area for both researchers and practioners. As mentioned before, for stochastic optimization problems, simulation is a viable approach. Multiple simulation replications must be performed in order to get a good estimate of $E_{\xi}[h(\theta_i,\xi)]$, which is the function value at parameter $\theta_i$. The standard approach to estimate this is via the sample mean
\begin{align}\label{eq:sm}
\overline {f_n} (\theta_i) = \frac{1}{n} ~  \sum_{j=1}^{n} h(\theta,\xi_j),
\end{align}
where $n$ is the number of simulation replications and $\xi_j$ is the $j$th sample of randomness. As $n \to \infty$, $\overline{ f_n} (\theta_i) \to E_{\xi}[h(\theta_i,\xi)]$. The primary concerns in stochastic optimization via simulation are 
\begin{inparaenum}[\bfseries (i)]
	\item $n$ must be large enough to get a good estimate of  $E_{\xi}[h(\theta_i,\xi)]$, which has an impact on the final solution that the optimization procedure needs to find; and
	\item The above procedure must be applied for many different parameters, i.e., $\theta$'s in order to find the best $\theta$.
\end{inparaenum}
Hence one of the key criteria for comparing different simulation-based optimization approaches is through the total number of simulations performed by them to attain a specific function value. Note that different approaches may require different number of simulations per  iteration. In this section we present methods only for Continuous and Discrete optimization via simulation problems which often occur in practise. However, hybrid optimization problems are not frequently encountered. From  now on, we consider the setting of optimization problems mentioned in this section as the stochastic optimization setting presented in section \ref{sc:objclass}, i.e., when objective function is an expected value over certain noisy cost measurements. 
\subsection{Discrete optimization via simulation}
Optimization problems for which $\Theta$ is a discrete set are known as discrete optimization via simulation problems. In the discrete case $\theta$, can take only countable (finite or infinite) number of values. Discrete optimization problems are some times take the form of \emph{combinatorial optimization} problems and they have applications in resource allocation, network routing, policy planning etc.
In this section we consider the case of $\Theta$ being finite i.e., $\Theta = \{\theta_{1},\theta_{2},\ldots,\theta_{k}\}$ where $k \in \mathbb{N}$. Discrete optimization problems are divided into two sub-classes when the feasible region is  either small (often less than 100) or is large. We present optimization methods in the literature separately for each class.\\
%\begin{enumerate}
\subsubsection{$\Theta$ is small}
In this case we can simulate all possible solutions and select the best among them. However, unlike in deterministic optimization, simulating the system only once for each parameter is not enough since the objective function is noisy in the stochastic optimization setting. Hence the main question is how to conduct multiple simulations effectively for each parameter in order to determine the  best parameter $\theta$.  Two popular methods in literature for this case are Ranking and Selection (R\&S)\cite{bech} and Multiple comparison procedures (MCP) \cite{mcp}. These methods are well suited for simulation since  the underlying assumptions such as normality and independence of observations can be met through careful selection procedures.
Traditional methods in this setting are applicable for a maximum set size of 20 while some recent techniques allow more. 
\begin{enumerate}

@@

where $a_n$ is the step-size that satisfies standard stochastic approximation conditions (see (A12) in Section \ref{sec:2rdsa-results}), and $\widehat\nabla f(\theta_n)$ and $\overline H_n$ are estimates of the gradient and Hessian, respectively. Thus, \eqref{eq:newton} can be considered as  the stochastic version of the well-known Newton method for optimization. Stochastic Newton methods are often more accurate than simple gradient search schemes. A key early work in stochastic Newton methods  is given in \cite{anbar1978stochastic}. A sleeker `ODE' based convergence argument might be facilitated by \cite{smale1976convergent}.
